Heading Cross Corr

### 2023-06-27 Fish Data Analysis/Heading Cross Corr.qmd
Changing Cross Corr

  out_corrs <- out_df$max_corr
  out_lags <- out_df$max_corr_lag

  length(out_corrs) <- length(x)
  length(out_lags) <- length(x)

@@

Okay so now a specific correaltion version

@@

raw_heading_corrs <- raw_fish_comp_data_combo %>% #filter(Data_ID == "2021_8_3_11" & Fish1 == "individual8"  & Fish2 == "individual7") %>%
                                          group_by(Year,Month,Day,Trial,Fish1,Fish2) %>%
                                          mutate(len_run = sum(!is.na(Distance))) %>%
                                          ungroup() %>%
                                          filter(len_run > 2) %>%
                                          group_by(Year,Month,Day,Trial,Fish1,Fish2) %>%
                                          mutate(corrs = get_corrs_lags_ben(Fish1_Yaw_Heading,Fish2_Yaw_Heading)[[1]],
                                                 lags = get_corrs_lags_ben(Fish1_Yaw_Heading,Fish2_Yaw_Heading)[[2]])

raw_heading_corrs_sum <- raw_heading_corrs %>% filter(lags >= 0) %>%
                                       group_by(Year,Month,Day,Trial,Data_ID,Fish1,Fish2, Flow, Ablation, Darkness, Flow_Ablation_Darkness) %>%
                                       summarise(max_corr = first(max(corrs, na.rm = TRUE)),
                                                 max_corr_lag = first(lags[na.omit(corrs == max_corr)]),
                                                 max_corr_distance = first(Distance[na.omit(corrs == max_corr)])) %>%
                                       group_by(Flow, Ablation, Darkness) %>%
                                       mutate(Mean_Max_Corr = mean(max_corr, na.rm = T), SD_Max_Corr = sd(max_corr, na.rm = T),
                                              Mean_Max_Corr_Lag = mean(max_corr_lag, na.rm = T), SD_Max_Corr_Lag = sd(max_corr_lag, na.rm = T),
                                              Mean_Max_Corr_Distance = mean(max_corr_distance, na.rm = T), SD_Max_Corr_Distance = sd(max_corr_distance, na.rm = T)) %>%
                                       ungroup()
```

@@

ggplot(raw_heading_corrs_sum %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = max_corr,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth/2, "npc")) +
  geom_point(aes(y = Mean_Max_Corr), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Max_Corr-SD_Max_Corr, ymax=Mean_Max_Corr+SD_Max_Corr), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Max Correlation") +
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

ggplot(raw_heading_corrs_sum %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = max_corr_lag,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth/4, "npc")) +
  geom_point(aes(y = Mean_Max_Corr_Lag), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Max_Corr_Lag-SD_Max_Corr_Lag, ymax=Mean_Max_Corr_Lag+SD_Max_Corr_Lag), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Lag at Max Correlation") +
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

ggplot(raw_heading_corrs_sum %>% filter(Flow == "Still Water"),
       aes(x = max_corr, y = max_corr_distance,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_point() +
  geom_smooth(se = F, method="glm") +
  guides(fill = guide_legend(title = "Condition")) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  xlab("Max Correlation") +
  ylab("Distance at Max Correlation") +
  xlim(0,1)+
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.x = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

max_corr_glmer <- lmer(max_corr ~ Ablation + Darkness + (1|Data_ID), data = raw_heading_corrs_sum %>% filter(Flow == "Still Water"))
Anova(max_corr_glmer)

max_corr_vs_dist_glmer <- lmer(max_corr_distance ~ max_corr*(Ablation + Darkness) + (1|Data_ID), data = raw_heading_corrs_sum %>% filter(Flow == "Still Water"))
Anova(max_corr_vs_dist_glmer)

>>>>

  out_corrs <- rep(NA,length(x))
  out_lags <- rep(NA,length(x))

  for (i in 1:length(out_df$window_start)) {
    out_corrs[out_df$window_start[i]] <- out_df$max_corr[i]
    out_lags[out_df$window_start[i]] <- out_df$max_corr_lag[i]
  }

@@

Okay so now a specific correlation version

@@

raw_heading_corrs <- raw_fish_comp_data_combo %>% #filter(Data_ID == "2021_8_3_11" & Fish1 == "individual8"  & Fish2 == "individual7") %>%
                                          group_by(Year,Month,Day,Trial,Fish1,Fish2) %>%
                                          mutate(len_run = sum(!is.na(Distance))) %>%
                                          ungroup() %>%
                                          filter(len_run > 2) %>%
                                          group_by(Year,Month,Day,Trial,Fish1,Fish2) %>%
                                          mutate(corrs = windowed_correlation_finder(Fish1_Yaw_Heading,Fish2_Yaw_Heading)$ccf,
                                                 lags = windowed_correlation_finder(Fish1_Yaw_Heading,Fish2_Yaw_Heading)$lags)

raw_heading_corrs_sum <- raw_heading_corrs %>% filter(lags >= 0) %>%
                                       group_by(Year,Month,Day,Trial,Data_ID,Fish1,Fish2, Flow, Ablation, Darkness, Flow_Ablation_Darkness) %>%
                                       summarise(max_corr = first(max(corrs, na.rm = TRUE)),
                                                 max_corr_lag = first(lags[na.omit(corrs == max_corr)]),
                                                 max_corr_distance = first(Distance[na.omit(corrs == max_corr)])) %>%
                                       group_by(Flow, Ablation, Darkness) %>%
                                       mutate(Mean_Max_Corr = mean(max_corr, na.rm = T), SD_Max_Corr = sd(max_corr, na.rm = T),
                                              Mean_Max_Corr_Lag = mean(max_corr_lag, na.rm = T), SD_Max_Corr_Lag = sd(max_corr_lag, na.rm = T),
                                              Mean_Max_Corr_Distance = mean(max_corr_distance, na.rm = T), SD_Max_Corr_Distance = sd(max_corr_distance, na.rm = T)) %>%
                                       ungroup()

raw_heading_corrs_graphing <- raw_heading_corrs %>% filter(!is.na(Distance) & !is.na(corrs))%>%
                                       group_by(Flow, Ablation, Darkness) %>%
                                       mutate(Mean_Corr = mean(corrs, na.rm = T), SD_Corr = sd(corrs, na.rm = T),
                                              Mean_Lag = mean(lags, na.rm = T), SD_Lag = sd(lags, na.rm = T))

@@

ggplot(raw_heading_corrs_graphing %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = corrs,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_jitter(height = 0, alpha = 0.2)+
  #stat_dots(side = "both", binwidth = unit(dot_binwidth/2, "npc")) +
  geom_point(aes(y = Mean_Corr), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Corr-SD_Corr, ymax=Mean_Corr+SD_Corr), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Max Correlation") +
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

ggplot(raw_heading_corrs_graphing %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = lags,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_jitter(height = 0, alpha = 0.2)+
  #stat_dots(side = "both", binwidth = unit(dot_binwidth/4, "npc")) +
  geom_point(aes(y = Mean_Lag), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Lag-SD_Lag, ymax=Mean_Lag+SD_Lag), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Lag at Max Correlation") +
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

ggplot(raw_heading_corrs_graphing %>% filter(Flow == "Still Water"),
       aes(x = Distance, y = corrs,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_point(alpha = 0.2) +
  geom_smooth(se = F, method="glm") +
  guides(fill = guide_legend(title = "Condition")) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  xlab("Distance") +
  ylab("Correlation") +
  #xlim(0,1)+
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.x = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

ggplot(raw_heading_corrs_graphing %>% filter(Flow == "Still Water"),
       aes(x = Distance, y = lags,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_point(alpha = 0.2) +
  geom_smooth(se = F, method="glm") +
  guides(fill = guide_legend(title = "Condition")) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  xlab("Distance") +
  ylab("Best Lag") +
  #xlim(0,1)+
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.x = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

corr_glmer <- lmer(corrs ~ 0+Ablation + Darkness + (1|Data_ID), data = raw_heading_corrs_graphing %>% filter(Flow == "Still Water"))
summary(corr_glmer)
Anova(corr_glmer)

corr_vs_dist_glmer <- lmer(corrs ~ 0+Distance*(Ablation + Darkness) + (1|Data_ID), data = raw_heading_corrs_graphing %>% filter(Flow == "Still Water"))
summary(corr_vs_dist_glmer)
Anova(corr_vs_dist_glmer)
